Automated Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{NSF Grant ???} }

### 2021-03-31 paper/paper_new.tex
Committing to pull
Added histogram (without labels yet)

\subsection{Brightness/Uniformity Results?}
\textbf{Todo}: Need standard deviations here, too. To show that the
differences are significant and meaningful. Clearly the trend is there.\newline
It looks like we should leave out Uniformity.

\begin{verbatim}
Mean intensity in bounding box | Count

dark: 153.94935240158551 | 1800
normal: 168.2924981358199 | 5186
bright: 177.68854540643943 | 242
\end{verbatim}
\begin{verbatim}
Standard Deviations for:
    Uniform: 12.554834863869324
    Not Uniform: 11.312181711328828
\end{verbatim}

>>>>

\subsection{Brightness/Uniformity Results?}
\begin{figure}[H]
  \centering
  \includegraphics[width=\linewidth]{images/histo}
  \caption{Histogram for brightness.}
\end{figure}
\textbf{Todo}: It looks like we should leave out Uniformity.

\begin{verbatim}
Mean intensity in bounding box | Std
        | Count

dark: 153.94935240158566 |
        15.526143315470392 | 1800
normal: 168.2924981358199 |
        14.214506494349248 | 5186
bright: 177.68854540643952 |
        12.401282979349904 | 242
\end{verbatim}
\begin{verbatim}
Standard Deviations for:
    Uniform: 12.554834863869324
    Not Uniform: 11.312181711328828
\end{verbatim}
